---
title: "CovidData"
author: "Ziyade CHABI MACO"
date: "2024-12-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Python part
#Link1: Exercise 1:first 5 rows from COVID-19 dataset, printing the dataset information and check the missing values.
```{r print}

# Charger les bibliothèques nécessaires
library(dplyr)
library(readr)

# Charger les données à partir du fichier CSV en ligne
covid_data <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-17-2020.csv")

# Afficher les premières lignes des données
print("Dataset:")
print(head(covid_data))

# Afficher les informations sur le dataset
cat("\nDataset information:\n")
glimpse(covid_data)

# Informations sur les données manquantes
cat("\nMissing data information:\n")
missing_data <- colSums(is.na(covid_data))
print(missing_data)

```

#Python part
#Link1: Exercise 2:Getting the latest number of confirmed, deaths, recovered and active cases of Novel Coronavirus (COVID-19) Country wise.
```{r print}

# Load necessary library
library(dplyr)

# Read the CSV file directly from the URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-17-2020.csv"
covid_data <- read.csv(url)

# Calculate the 'Active' cases
covid_data$Active <- covid_data$Confirmed - covid_data$Deaths - covid_data$Recovered

# Group by 'Country/Region' and summarize the data
result <- covid_data %>%
  group_by(Country.Region) %>%
  summarise(
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Deaths = sum(Deaths, na.rm = TRUE),
    Recovered = sum(Recovered, na.rm = TRUE),
    Active = sum(Active, na.rm = TRUE)
  )

# Print the result
print(result)

```

#Python part
#Link1: Exercise 3:Getting the latest number of confirmed, deaths, recovered and active cases of Novel Coronavirus (COVID-19) Country wise.
```{r print}
# Load necessary libraries
library(dplyr)

# Read the CSV file directly from the URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-16-2020.csv"
covid_data <- read.csv(url)

# Group by 'Country/Region' and 'Province/State' and take the maximum of 'Confirmed', 'Deaths', and 'Recovered'
data <- covid_data %>%
  group_by(Country.Region, Province.State) %>%
  summarise(
    Confirmed = max(Confirmed, na.rm = TRUE),
    Deaths = max(Deaths, na.rm = TRUE),
    Recovered = max(Recovered, na.rm = TRUE)
  )

# Print all rows (to avoid truncation, similar to `pd.set_option('display.max_rows', None)` in Python)
print(data, n = Inf)


```

#Python part
#Link1: Exercise 4:Getting the Chinese province wise cases of confirmed, deaths and recovered cases of Novel Coronavirus (COVID-19).
```{r print}
# Load necessary libraries
library(dplyr)

# Read the CSV file directly from the URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-17-2020.csv"
covid_data <- read.csv(url)

# Group by 'Country/Region' and calculate the sum of 'Confirmed', 'Deaths', and 'Recovered'
data <- covid_data %>%
  group_by(Country.Region) %>%
  summarise(
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Deaths = sum(Deaths, na.rm = TRUE),
    Recovered = sum(Recovered, na.rm = TRUE)
  )

# Filter rows where 'Confirmed' equals 'Deaths'
result <- data %>%
  filter(Confirmed == Deaths) %>%
  select(Country.Region, Confirmed, Deaths)

# Sort by 'Confirmed' in descending order
result <- result %>%
  arrange(desc(Confirmed))

# Keep rows where 'Confirmed' > 0 and reset the row index
result <- result %>%
  filter(Confirmed > 0) %>%
  mutate(Row = row_number()) %>% # Adds a row index
  select(-Row)                  # Optional: drop the row index column

# Print the result
print(result)


```

#Python part
#Link1: Exercise 5:Getting the latest country wise deaths cases of Novel Coronavirus (COVID-19).
```{r print}
# Load necessary libraries
library(dplyr)

# Read the CSV file directly from the URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-17-2020.csv"
covid_data <- read.csv(url)

# Group by 'Country/Region' and calculate the sum of 'Confirmed', 'Deaths', and 'Recovered'
data <- covid_data %>%
  group_by(Country.Region) %>%
  summarise(
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Deaths = sum(Deaths, na.rm = TRUE),
    Recovered = sum(Recovered, na.rm = TRUE)
  )

# Filter rows where Deaths > 0 and select 'Country/Region' and 'Deaths'
result <- data %>%
  filter(Deaths > 0) %>%
  select(Country.Region, Deaths)

# Print the result
print(result)


```

#Python part
#Link1: Exercise 6:listing countries with no cases of Novel Coronavirus (COVID-19) recovered.
```{r print}
# Load necessary libraries
library(dplyr)

# Read the CSV file directly from the URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-17-2020.csv"
covid_data <- read.csv(url)

# Group by 'Country/Region' and calculate the sum of 'Confirmed', 'Deaths', and 'Recovered'
data <- covid_data %>%
  group_by(Country.Region) %>%
  summarise(
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Deaths = sum(Deaths, na.rm = TRUE),
    Recovered = sum(Recovered, na.rm = TRUE)
  )

# Filter rows where 'Recovered' is 0 and select relevant columns
result <- data %>%
  filter(Recovered == 0) %>%
  select(Country.Region, Confirmed, Deaths, Recovered)

# Print the result
print(result)

```

#Python part
#Link1: Exercise 7:listing countries with all cases of Novel Coronavirus (COVID-19) died.
```{r print}
# Charger les bibliothèques nécessaires
library(dplyr)
library(readr)

# Charger les données à partir du fichier CSV en ligne
covid_data <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-17-2020.csv")

# Grouper les données par 'Country/Region' et calculer les sommes pour 'Confirmed', 'Deaths' et 'Recovered'
data <- covid_data %>%
  group_by(`Country/Region`) %>%
  summarise(
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Deaths = sum(Deaths, na.rm = TRUE),
    Recovered = sum(Recovered, na.rm = TRUE)
  )

# Filtrer les pays où Confirmed == Deaths
result <- data %>%
  filter(Confirmed == Deaths) %>%
  select(`Country/Region`, Confirmed, Deaths)

# Trier les résultats par Confirmed dans l'ordre décroissant
result <- result %>%
  arrange(desc(Confirmed))

# Filtrer les pays avec un nombre de cas Confirmed > 0
result <- result %>%
  filter(Confirmed > 0)

# Réinitialiser les index
result <- result %>%
  mutate(row_id = row_number()) %>%
  select(-row_id)

# Afficher les résultats finaux
print(result)


```

#Python part
#Link1: Exercise 8:listing countries with all cases of Novel Coronavirus (COVID-19) recovered.
```{r print}
# Load necessary libraries
library(dplyr)

# Read the CSV file directly from the URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-17-2020.csv"
covid_data <- read.csv(url)

# Group by 'Country/Region' and calculate the sum of 'Confirmed', 'Deaths', and 'Recovered'
data <- covid_data %>%
  group_by(Country.Region) %>%
  summarise(
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Deaths = sum(Deaths, na.rm = TRUE),
    Recovered = sum(Recovered, na.rm = TRUE)
  )

# Filter rows where 'Confirmed' equals 'Recovered'
result <- data %>%
  filter(Confirmed == Recovered) %>%
  select(Country.Region, Confirmed, Recovered)

# Sort by 'Confirmed' in descending order
result <- result %>%
  arrange(desc(Confirmed))

# Keep rows where 'Confirmed' > 0 and reset the row index
result <- result %>%
  filter(Confirmed > 0)

# Print the result
print(result)


```

#Python part
#Link1: Exercise 9:Getting the top 10 countries data (Last Update, Country/Region, Confirmed, Deaths, Recovered) of Novel Coronavirus (COVID-19).


```{r print}

# Load necessary libraries
library(dplyr)

# Read the CSV file directly from the URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-18-2020.csv"
covid_data <- read.csv(url)

# Select only relevant columns
covid_data <- covid_data %>%
  select(Last.Update, Country.Region, Confirmed, Deaths, Recovered)

# Group by 'Country/Region', find the maximum value for each group, and sort by 'Confirmed' in descending order
result <- covid_data %>%
  group_by(Country.Region) %>%
  summarise(
    Last.Update = max(Last.Update, na.rm = TRUE),
    Confirmed = max(Confirmed, na.rm = TRUE),
    Deaths = max(Deaths, na.rm = TRUE),
    Recovered = max(Recovered, na.rm = TRUE)
  ) %>%
  arrange(desc(Confirmed)) %>%
  slice(1:10)  # Get the top 10 rows

# Print the result
print(result)

```

#Python part
#Link1: Exercise 10:create a plot (lines) of total deaths, confirmed, recovered and active cases Country wise where deaths greater than 150.
```{r print}
# Load necessary libraries
library(dplyr)
library(ggplot2)

# Read the CSV file directly from the URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-19-2020.csv"
covid_data <- read.csv(url)

# Select only the relevant columns
covid_data <- covid_data %>%
  select(Last.Update, Country.Region, Confirmed, Deaths, Recovered)

# Create the 'Active' column
covid_data <- covid_data %>%
  mutate(Active = Confirmed - Deaths - Recovered)

# Group by 'Country/Region' and calculate the sum of relevant columns
r_data <- covid_data %>%
  group_by(Country.Region) %>%
  summarise(
    Deaths = sum(Deaths, na.rm = TRUE),
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Recovered = sum(Recovered, na.rm = TRUE),
    Active = sum(Active, na.rm = TRUE)
  )

# Filter countries with more than 50 deaths
r_data <- r_data %>%
  filter(Deaths > 150) %>%
  arrange(desc(Deaths))

# Plot the data
ggplot(r_data, aes(x = Country.Region)) +
  geom_line(aes(y = Deaths, color = "Deaths"), group = 1) +
  geom_line(aes(y = Confirmed, color = "Confirmed"), group = 1) +
  geom_line(aes(y = Recovered, color = "Recovered"), group = 1) +
  geom_line(aes(y = Active, color = "Active"), group = 1) +
  labs(
    title = "Total Deaths (>150), Confirmed, Recovered, and Active Cases by Country",
    x = "Country",
    y = "Number of Cases"
  ) +
  scale_color_manual(
    name = "Legend",
    values = c("Deaths" = "red", "Confirmed" = "green", "Recovered" = "blue", "Active" = "black")
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )

```

#Python part
#Link1: Exercise 11:visualize the state/province wise death cases of Novel Coronavirus (COVID-19) in USA.
```{r print}
# Load necessary libraries
library(dplyr)
library(plotly)

# Read the COVID-19 data from the provided URL
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-17-2020.csv"
covid_data <- read.csv(url)

# Filter data for the US and drop unnecessary columns
us_data <- covid_data %>%
  filter(Country.Region == "US") %>%
  select(-Country.Region, -Latitude, -Longitude)

# Remove rows where all numeric values are zero
us_data <- us_data %>%
  filter(rowSums(across(where(is.numeric), ~ .x), na.rm = TRUE) > 0)

# Group by 'Province/State' and sum 'Deaths'
us_data <- us_data %>%
  group_by(Province.State) %>%
  summarise(Deaths = sum(Deaths, na.rm = TRUE))

# Filter states with more than 0 deaths
us_data_death <- us_data %>%
  filter(Deaths > 0)

# Create a bar plot using plotly
state_fig <- plot_ly(
  data = us_data_death,
  x = ~Province.State,
  y = ~Deaths,
  type = "bar",
  text = ~Deaths,
  textposition = "outside",
  marker = list(color = "red")
) %>%
  layout(
    title = "State-wise Deaths Reported of COVID-19 in USA",
    xaxis = list(title = "Province/State"),
    yaxis = list(title = "Number of Deaths"),
    showlegend = FALSE
  )

# Show the plot
state_fig

```

#Python part
#Link1: Exercise 12:visualize the state/province wise Active cases of Novel Coronavirus (COVID-19) in USA.
```{r print}
# Charger les bibliothèques nécessaires
library(dplyr)
library(readr)
library(ggplot2)

# Charger les données à partir du fichier CSV en ligne
covid_data <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-18-2020.csv")

# Ajouter une colonne 'Active' calculée
covid_data <- covid_data %>%
  mutate(Active = Confirmed - Deaths - Recovered)

# Filtrer les données pour les États-Unis et supprimer des colonnes inutiles
us_data <- covid_data %>%
  filter(`Country/Region` == "US") %>%
  select(-`Country/Region`, -Latitude, -Longitude)

# Supprimer les lignes avec une somme des valeurs <= 0
us_data <- us_data[rowSums(select_if(us_data,is.numeric), na.rm = TRUE) > 0, ]

# Grouper par 'Province/State' et sommer les cas 'Active'
us_data <- us_data %>%
  group_by(`Province/State`) %>%
  summarise(Active = sum(Active, na.rm = TRUE))

# Filtrer les états avec des cas 'Active' > 0
us_data_death <- us_data %>%
  filter(Active > 0)

# Créer un graphique à barres avec ggplot2
state_fig <- ggplot(us_data_death, aes(x = reorder(`Province/State`, -Active), y = Active, label = Active)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(vjust = -0.5, color = "black") +
  labs(
    title = "State wise recovery cases of COVID-19 in USA",
    x = "Province/State",
    y = "Active Cases"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Afficher le graphique
print(state_fig)

```

#Python part
#Link1: Exercise 13:Visualize the state/province wise combine number of confirmed, deaths, recovered, active Novel Coronavirus (COVID-19) cases in USA.
```{r print}
# Charger les bibliothèques nécessaires
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)

# Charger les données à partir du fichier CSV en ligne
covid_data <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-19-2020.csv")

# Ajouter une colonne 'Active' calculée
covid_data <- covid_data %>%
  mutate(Active = Confirmed - Deaths - Recovered)

# Filtrer les données pour les États-Unis et supprimer les colonnes inutiles
combine_us_data <- covid_data %>%
  filter(`Country/Region` == "US") %>%
  select(-`Country/Region`, -Latitude, -Longitude)

# Supprimer les lignes avec une somme des valeurs <= 0
combine_us_data <- combine_us_data %>%
  filter(rowSums(select_if(., is.numeric), na.rm = TRUE) > 0)

# Grouper par 'Province/State' et sommer les colonnes numériques
combine_us_data <- combine_us_data %>%
  group_by(`Province/State`) %>%
  summarise(
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Deaths = sum(Deaths, na.rm = TRUE),
    Recovered = sum(Recovered, na.rm = TRUE),
    Active = sum(Active, na.rm = TRUE)
  )

# Transformer les données en format long
combine_us_data_long <- combine_us_data %>%
  pivot_longer(
    cols = c(Confirmed, Deaths, Recovered, Active),
    names_to = "Case",
    values_to = "Count"
  )

# Créer un graphique à barres avec ggplot2
fig <- ggplot(combine_us_data_long, aes(x = reorder(`Province/State`, -Count), y = Count, fill = Case, label = Count)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(position = position_dodge(width = 0.9), vjust = -0.5, size = 3) +
  labs(
    title = "USA State wise combine number of confirmed, deaths, recovered, active COVID-19 cases",
    x = "Province/State",
    y = "Count"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Afficher le graphique
print(fig)

```

#Python part
#Link1: Exercise 14:visualize Worldwide Confirmed Novel Coronavirus (COVID-19) cases over time.
```{r print}
# Charger les bibliothèques nécessaires
library(dplyr)
library(readr)
library(ggplot2)

# Charger les données à partir du fichier CSV en ligne
covid_data <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-19-2020.csv")

# Grouper les données par 'Last Update' et sommer 'Confirmed' et 'Deaths'
grouped <- covid_data %>%
  group_by(`Last Update`) %>%
  summarise(
    Confirmed = sum(Confirmed, na.rm = TRUE),
    Deaths = sum(Deaths, na.rm = TRUE)
  )

# Créer un graphique de ligne pour les cas confirmés dans le temps
fig <- ggplot(grouped, aes(x = as.POSIXct(`Last Update`, format = "%Y-%m-%d %H:%M:%S"), y = Confirmed)) +
  geom_line(color = "steelblue", size = 1) +
  labs(
    title = "Worldwide Confirmed Novel Coronavirus (COVID-19) Cases Over Time",
    x = "Last Update",
    y = "Confirmed Cases"
  ) +
  theme_minimal()

# Afficher le graphique
print(fig)

```

