---
title: 'dplyr basics: More smooth data exploration'
author: "Ziyade CHABI MACO"
date: "2024-12-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#link3.Exercise 1: Load required packages and data.
```{r }
# Load necessary libraries

library(dplyr)
install.packages("AER")
library(AER)

# Load the Fertility dataset
data("Fertility")

# Glimpse at the data
glimpse(Fertility)


```

# link3.Exercise 2: Select rows 35 to 50 and display age and work columns
```{r }

library(dplyr)

Fertility %>%
  slice(35:50) %>%
  select(age, work)

```

#link3.Exercise 3: Select the last row in the dataset.
```{r }
library(dplyr)

Fertility %>%
  slice(n())  # Selects the last row

```

#link3.Exercise 4: Count how many women proceeded to have a third child.
```{r}
library(dplyr)
Fertility %>%
  filter(morekids == 1) %>%  # `morekids` column indicates if the woman had a third child
  count()

```

#link3.Exercise 5: Determine the most common gender combination for the first two children.
```{r }
library(dplyr)
Fertility %>%
  count(gender1, gender2) %>%  # Count combinations of `gender1` and `gender2`
  arrange(desc(n)) %>%        # Sort in descending order
  slice(1)                    # Select the most common combination


```

#link3.Exercise 6: Proportion of women working four weeks or less in 1979 by racial composition.
```{r }
library(dplyr)
Fertility %>%
  group_by(afam, hispanic, other) %>%
  summarise(mean(work <= 4))
  
```

#link3.Exercise 7: Proportion of women aged 22–24 with a boy as their firstborn.
```{r }
Fertility %>%
  filter(age >= 22, age <= 24) %>%          # Filter for women aged 22 to 24
  summarise(proportion_boys = mean(gender1 == "male", na.rm = TRUE))  # Calculate proportion of firstborn boys

```

#link3.Exercise 8: Add a new column for age squared.
```{r }
Fertility <- Fertility %>%
  mutate(age_squared = age^2)

# Display the updated dataset
glimpse(Fertility)

```

#link3.Exercise 9: Racial composition with the lowest proportion of boys for their firstborn.
```{r }
Fertility %>%
  group_by(afam, hispanic, other) %>%
  summarise(prop_boys_fb = mean(gender1 == "male"), n = n()) %>%
  arrange(prop_boys_fb)

```

#link3.Exercise 10: proportion of women who have a third child by gender combination of the first two children
```{r }
Fertility %>%
  group_by(gender1, gender2) %>%
  summarise(mean(morekids == "yes"))

```

